---
title: "stCEG README"
output:
  github_document:
    html_preview: true
always_allow_html: false
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
install.packages("webshot2")
knitr::opts_chunk$set(
  out.width = 1200)
```

# stCEG

<!-- badges: start -->
<!-- badges: end -->

The goal of `stCEG` is to facilitate the creation of Chain Event Graphs over spatial areas. It allows users to fully customise both the structure and underlying model of the Chain Event Graph, offering a high degree of flexibility for tailored analyses.

## Installation

You can install the stable version of `stCEG` from CRAN with:
```{r, eval = FALSE}
install.packages("stCEG")
```

Or the development version from [GitHub](https://github.com/) with:
```{r}
remotes::install_github("holliecalley/stCEG")
```

## Usage

With the `stCEG` package, it is simple for a user to create an event tree from a given dataset, colour it to turn it into a staged tree, specify priors over this, and then convert this into a Chain Event Graph (CEG). The package also allows for model comparison and the creation of maps based on spatial CEGs, as well as a `Shiny` user-interface.

```{r, screenshot.force=TRUE}
library(stCEG)
data <- homicides
event_tree <- create_event_tree(data, columns = c(1,2,4,5), "both")
event_tree$eventtree
```

```{r,  screenshot.force=TRUE}
coloured_tree <- ahc_colouring(event_tree)
coloured_tree$stagedtree
```

```{r}
tree_priors <- specify_priors(coloured_tree, prior_type = "Uniform", ask_edit = FALSE)
```
```{r,  screenshot.force=TRUE, screenshot.vwidth=1600}
staged_tree <- staged_tree_prior(coloured_tree, tree_priors)
staged_tree$stagedtree
```

```{r,  screenshot.force=TRUE}
ceg <- create_ceg(staged_tree, view_table = FALSE)
ceg$ceg
```
